Hunting the Orphan Stream Host: The First High-Resolution Spectroscopic\\ Analysis on the Orphan Stream

### 2012-11-15 2012-oss-hrs/draft-oss.tex
updated 2012 oss hrs

\title{Chemistry of the Orphan Stream II: The First High-Resolution Spectroscopic Analysis on the Orphan Stream}

@@

\begin{abstract}
test
\end{abstract}

@@

\begin{deluxetable*}{lcccccccccl}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
& \multicolumn{4}{c}{This work}  &
& \multicolumn{4}{c}{Literature} & \\
  \cline{2-5} \cline{7-10} \\
  \colhead{Star} &
  \colhead{$T_{\mbox{eff}}$} &
 \colhead{$\log{(g)}$} &
	\colhead{[Fe/H]} &
	\colhead{$v_t$} 
	&&
	\colhead{$T_{\mbox{eff}}$} &
	\colhead{$\log{(g)}$} &
	\colhead{[Fe/H]} &
	\colhead{$v_t$} &
	\colhead{Reference} \\
 & [K] & [dex] & [dex] & [km s$^{-1}$] 
&& [K] & [dex] & [dex] & [km s$^{-1}$] & 
}
\startdata
HD 136316 & $4370$ & $1.00$ & $-1.99$ & $1.95$ 
         && $4469$ & $1.29$ & $-1.74$ & $1.90$ & \citet{Gratton;et-al_2000} \\
HD 141531 & $4330$ & $0.90$ & $-1.74$ & $1.80$ 
         && $4335$ & $1.11$ & $-1.62$ & $1.50$ & \citet{Gratton;et-al_2000} \\
HD 142948 & $4870$ & $2.20$ & $-0.78$ & $1.45$ 
         && $4713$ & $2.17$ & $-0.77$ & $1.38$ & \citet{Gratton;et-al_2000} \\
HD 41667  & $4600$ & $1.70$ & $-1.23$ & $1.50$  
         && $4605$ & $1.88$ & $-1.16$ & $1.44$ & \citet{Gratton;et-al_2000} \\
HD 44007  & $4800$ & $1.80$ & $-1.77$ & $1.55$ 
         && $4850$ & $2.00$ & $-1.71$ & $2.20$ & \citet{Fulbright_2000} \\
HD 47536  & & & & 
         &&\nodata &\nodata & \nodata &\nodata & \\
HD 76932  & & & & 
         && $5900$ & $4.20$ & $-0.70$ & $1.25$ & \citet{Fulbright_2000} \\
HD 84903  & & & & 
         && $4500$ & $0.80$ & $-2.60$ & $2.00$ & \citet{Francois_1996} \\
HD 59984  & & & & 
         && & & & & Binary system.\\
HD 60060  & & & & 
         &&\nodata &\nodata & \nodata &\nodata & \\
HD 60228  & & & & 
         &&\nodata &\nodata & \nodata &\nodata & \\
OSS 1     & 5040 & 2.80 & -1.22 & 1.40 && & & & & \\
OSS 2     & 4550 & 0.80 & -1.78 & 1.85 && & & & & \\
OSS 3     & 4780 & 1.55 & -1.79 & 1.70 && & & & & \\
OSS 4     & 4580 & 0.80 & -2.75 & 2.05 && & & & & \\
OSS 5     & 5250 & 3.00 & -0.80 & 1.85 && & & & & 
\enddata
\end{deluxetable*}

>>>>

\title{Hunting the Orphan Stream Host: The First High-Resolution Spectroscopic\\ Analysis on the Orphan Stream}

@@

\begin{abstract}
\#todo
\end{abstract}

@@

\begin{deluxetable*}{lcccccccccl}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
& \multicolumn{4}{c}{This work}  &
& \multicolumn{4}{c}{Literature} & \\
  \cline{2-5} \cline{7-10} \\
  \colhead{Star} &
  \colhead{$T_{\mbox{eff}}$} &
 \colhead{$\log{(g)}$} &
	\colhead{[Fe/H]} &
	\colhead{$v_t$} 
	&&
	\colhead{$T_{\mbox{eff}}$} &
	\colhead{$\log{(g)}$} &
	\colhead{[Fe/H]} &
	\colhead{$v_t$} &
	\colhead{Reference} \\
 & [K] & [dex] & [dex] & [km s$^{-1}$] 
&& [K] & [dex] & [dex] & [km s$^{-1}$] & 
}
\startdata
HD 136316 & $4370$ & $1.00$ & $-1.99$ & $1.95$ 
         && $4469$ & $1.29$ & $-1.74$ & $1.90$ & \citet{Gratton;et-al_2000} \\
HD 141531 & $4330$ & $0.90$ & $-1.74$ & $1.80$ 
         && $4335$ & $1.11$ & $-1.62$ & $1.50$ & \citet{Gratton;et-al_2000} \\
HD 142948 & $4870$ & $2.20$ & $-0.78$ & $1.45$ 
         && $4713$ & $2.17$ & $-0.77$ & $1.38$ & \citet{Gratton;et-al_2000} \\
HD 41667  & $4600$ & $1.70$ & $-1.23$ & $1.50$  
         && $4605$ & $1.88$ & $-1.16$ & $1.44$ & \citet{Gratton;et-al_2000} \\
HD 44007  & $4800$ & $1.80$ & $-1.77$ & $1.55$ 
         && $4850$ & $2.00$ & $-1.71$ & $2.20$ & \citet{Fulbright_2000} \\
OSS 1     & 5040 & 2.80 & $-$1.22 & 1.40 && & & & & \\
OSS 2     & 4550 & 0.80 & $-$1.78 & 1.85 && & & & & \\
OSS 3     & 4780 & 1.55 & $-$1.79 & 1.70 && & & & & \\
OSS 4     & 4580 & 0.80 & $-$2.75 & 2.05 && & & & & \\
OSS 5     & 5250 & 3.00 & $-$0.80 & 1.85 && & & & & 
\enddata
\end{deluxetable*}
